Unshuffling Permutations

### 2016-02-02 article.tex
add tikz arcs

@@

@@

@@

\begin{lemma}
  \label{lemma:matching}
  Let $\pi$ be a permutation. The following statements are equivalent:
  \begin{enumerate}
    \item The permutation $\pi$ is a square.
    \item There exists an oriented perfect matching $\vv{\mathcal{M}}$
    of $G_\pi$ that avoids \InclusionLL, \InclusionLR,\InclusionRL,\InclusionRR,
    \CrossingLR and \CrossingRL such that for any two distinct arcs $(a, a)$ and
    $(b, b')$ in $\vv{\mathcal{M}}$ we have $\pi(a) < \pi(b)$ if and only
    if $\pi(a') < \pi(b')$.
  \end{enumerate}
\end{lemma}

>>>>

\newcommand{\Crossing}{%
\begin{tikzpicture}[scale=0.09,inner sep=.8pt,node distance=.25cm,>=latex']%,>=stealth',->]
\draw node [draw,circle,fill=black] (U1)               {};
\draw node [draw,circle,fill=black] [right of=U1] (U2) {};
\draw node [draw,circle,fill=black] [right of=U2] (U3) {};
\draw node [draw,circle,fill=black] [right of=U3] (U4) {};
\draw [] (U1.north) .. controls ($ (U1.north) + (0,4) $) and ($ (U3.north) + (0,4) $) .. (U3.north);
\draw [] (U2.north) .. controls ($ (U2.north) + (0,4) $) and ($ (U4.north) + (0,4) $) .. (U4.north);
\end{tikzpicture}
}% end \Crossing

@@

\newcommand{\Inclusion}{%
\begin{tikzpicture}[scale=0.09,inner sep=.8pt,node distance=.25cm,>=latex']
\draw node [draw,circle,fill=black] (U1)               {};
\draw node [draw,circle,fill=black] [right of=U1] (U2) {};
\draw node [draw,circle,fill=black] [right of=U2] (U3) {};
\draw node [draw,circle,fill=black] [right of=U3] (U4) {};
\draw [] (U1.north) .. controls ($ (U1.north) + (0,4) $) and ($ (U4.north) + (0,4) $) .. (U4.north);
\draw [] (U2.north) .. controls ($ (U2.north) + (0,3) $) and ($ (U3.north) + (0,3) $) .. (U3.north);
\end{tikzpicture}
}% end \Inclusion

@@

\newcommand{\Precedence}{%
\begin{tikzpicture}[scale=0.09,inner sep=.8pt,node distance=.25cm,>=latex']
\draw node [draw,circle,fill=black] (U1)               {};
\draw node [draw,circle,fill=black] [right of=U1] (U2) {};
\draw node [draw,circle,fill=black] [right of=U2] (U3) {};
\draw node [draw,circle,fill=black] [right of=U3] (U4) {};
\draw [] (U1.north) .. controls ($ (U1.north) + (0,4) $) and ($ (U2.north) + (0,4) $) .. (U2.north);
\draw [] (U3.north) .. controls ($ (U3.north) + (0,4) $) and ($ (U4.north) + (0,4) $) .. (U4.north);
\end{tikzpicture}
}% end \Precedence

@@

\begin{lemma}
  \label{lemma:matching}
  Let $\pi$ be a permutation. The following statements are equivalent:
  \begin{enumerate}
    \item The permutation $\pi$ is a square.
    \item There exists an oriented perfect matching $\vv{\mathcal{M}}$
    of the linear graph $G_\pi$ that avoids
    \InclusionLL,~\InclusionLR,~\InclusionRL,~\InclusionRR,~\CrossingLR
    and \CrossingRL, and such that for any two distinct arcs $(a, a)$ and
    $(b, b')$ in $\vv{\mathcal{M}}$ we have $\pi(a) < \pi(b)$ if and only
    if $\pi(a') < \pi(b')$.
  \end{enumerate}
\end{lemma}
